Synpotic Soil Characterization

### 2024-10-23 3-reports/manuscript_figures.Rmd
clean up report

```{r v2-pca_gg, fig.width=10, fig.height=6}
## PCA plots overall
#gg_pca_overall = 
ggbiplot(pca_overall$pca_int, obs.scale = 1, var.scale = 1,
         groups = as.character(pca_overall$grp$region), 
         ellipse = TRUE, circle = FALSE, var.axes = TRUE, alpha = 0) +
  geom_point(size=4,stroke=1, alpha = 1,
             aes(shape = pca_overall$grp$region,
                 fill = groups))+ 
  scale_color_manual(values = c("#16879C", "#BB281E"))+
  scale_fill_manual(values = c("#16879C", "#BB281E"))+
  scale_shape_manual(values = c(23, 21))+
  labs(shape="",
       title = "Overall PCA, both regions",
       subtitle = "Surface horizons only")+
  theme_kp()+
  guides(fill = "none")+
  NULL

@@

```{r v2-pca_gg_regions, fig.width=10, fig.height=6}

gg_pca_wle = 
  ggbiplot(pca_overall_wle$pca_int, obs.scale = 1, var.scale = 1,
           groups = as.character(pca_overall_wle$grp$transect), 
           ellipse = TRUE, circle = FALSE, var.axes = TRUE, alpha = 1) +
  geom_point(size=3,stroke=1, alpha = 1,
             aes(shape = pca_overall_wle$grp$site,
                 color = groups))+ 
  scale_color_manual(breaks = c("upland", "transition", "wte", "wc"), 
                     values = pal_transect)+
#  xlim(-6,6)+
#  ylim(-4.5,4.5)+
  labs(shape="",
       title = "PCA: WLE",
       subtitle = "surface horizons")+
  theme_kp()+
  theme(legend.position = "top", legend.box = "vertical")+
  NULL

gg_pca_cb = 
  ggbiplot(pca_overall_cb$pca_int, obs.scale = 1, var.scale = 1,
           groups = as.character(pca_overall_cb$grp$transect), 
           ellipse = TRUE, circle = FALSE, var.axes = TRUE, alpha = 0) +
  geom_point(size=3,stroke=1, alpha = 1,
             aes(shape = pca_overall_cb$grp$site,
                 color = groups))+ 
  scale_color_manual(breaks = c("upland", "transition", "wte", "wc"), 
                     values = pal_transect)+
#  xlim(-5.5,7.5)+
#  ylim(-5,5)+
  labs(shape="",
       title = "PCA: CB",
       subtitle = "surface horizons")+
  theme_kp()+
  theme(legend.position = "top", legend.box = "vertical")+
  NULL

@@

@@

```{r analytesx-2, fig.height = 4, fig.width = 8}
data_combined_wide %>% 
  mutate(transect = factor(transect, levels = c("upland", "transition", "wc"))) %>% 
  ggplot(aes(x = transect, y = Fe))+
  geom_violin(aes(fill = transect), alpha = 0.4)+
  geom_jitter(width = 0.1)+
  labs(x = "",
       y = "Extractable Fe, μg/g")+
  facet_wrap(~region)+
  scale_fill_manual(values = pal_transect)+
  theme(legend.position = "none")

>>>>

```{r v2-pca_gg, fig.width=10, fig.height=6}
## PCA plots overall
#gg_pca_overall = 
ggbiplot(pca_overall$pca_int, obs.scale = 1, var.scale = 1, varname.size = 5,
         groups = as.character(pca_overall$grp$region), 
         ellipse = TRUE, circle = FALSE, var.axes = TRUE, alpha = 0) +
  geom_point(size=4,stroke=1, alpha = 1,
             aes(shape = pca_overall$grp$region,
                 fill = groups))+ 
  scale_color_manual(values = c("#16879C", "#BB281E"))+
  scale_fill_manual(values = c("#16879C", "#BB281E"))+
  scale_shape_manual(values = c(23, 21))+
  labs(shape="",
       title = "Overall PCA, both regions",
       subtitle = "Surface horizons only")+
  theme_kp()+
  guides(fill = "none")+
  NULL

@@

```{r v2-pca_gg_regions, fig.width=12, fig.height=7}

gg_pca_wle = 
  ggbiplot(pca_overall_wle$pca_int, obs.scale = 1, var.scale = 1, varname.size = 5,
           groups = as.character(pca_overall_wle$grp$transect), 
           ellipse = TRUE, circle = FALSE, var.axes = TRUE, alpha = 1) +
  geom_point(size=3,stroke=1, alpha = 1,
             aes(shape = pca_overall_wle$grp$site,
                 color = groups))+ 
  scale_color_manual(breaks = c("upland", "transition", "wte", "wc"), 
                     values = pal_transect)+
  xlim(-3, 5)+
  ylim(-2.5, 3.5)+
  labs(shape="",
       title = "PCA: WLE")+
  theme_kp()+
  theme(legend.position = "top", legend.box = "vertical")+
  NULL

gg_pca_cb = 
  ggbiplot(pca_overall_cb$pca_int, obs.scale = 1, var.scale = 1, varname.size = 5,
           groups = as.character(pca_overall_cb$grp$transect), 
           ellipse = TRUE, circle = FALSE, var.axes = TRUE, alpha = 0) +
  geom_point(size=3,stroke=1, alpha = 1,
             aes(shape = pca_overall_cb$grp$site,
                 color = groups))+ 
  scale_color_manual(breaks = c("upland", "transition", "wte", "wc"), 
                     values = pal_transect)+
  xlim(-5.5, 3)+
  ylim(-3, 3.5)+
  labs(shape="",
       title = "PCA: CB")+
  theme_kp()+
  theme(legend.position = "top", legend.box = "vertical")+
  NULL

gg_pca_regions = cowplot::plot_grid(gg_pca_wle , gg_pca_cb, nrow = 1)
gg_pca_regions

@@

ggbiplot::ggbiplot(pca_cluster$pca_int, obs.scale = 1, var.scale = 1, varname.size = 5,
                   groups = as.character(pca_cluster$grp$cluster), 
                   ellipse = F, circle = FALSE, var.axes = TRUE, alpha = 0) +
  geom_convexhull(aes(group = pca_cluster$grp$cluster,
                      fill = pca_cluster$grp$cluster), alpha = 0.2)+
  geom_point(size=4,stroke=1, alpha = 1,
             aes(shape = pca_cluster$grp$region,
                 fill = groups))+ 
  scale_shape_manual(values = c(23, 21))+
  scale_color_manual(values = pnw_palette("Sailboat", 3))+
  scale_fill_manual(values = pnw_palette("Sailboat", 3))+
  labs(fill="cluster",
       color = "cluster",
       shape = "region",
       title = "Overall PCA, both regions",
       subtitle = "Surface horizons only")+
  theme_kp()+
  NULL

@@

```{r analytesx-2, fig.height = 4, fig.width = 8, eval=FALSE}
data_combined_wide %>% 
  mutate(transect = factor(transect, levels = c("upland", "transition", "wc"))) %>% 
  ggplot(aes(x = transect, y = Fe))+
  geom_violin(aes(fill = transect), alpha = 0.4)+
  geom_jitter(width = 0.1)+
  labs(x = "",
       y = "Extractable Fe, μg/g")+
  facet_wrap(~region)+
  scale_fill_manual(values = pal_transect)+
  theme(legend.position = "none")
